---
title: "PSY5013_Homework5"
output: html_document
---

### Assignment 5: Question 2
There are 11 variables in the data set “hsb_mar.xls”. Note that although dataset contains 200 cases, six of the variables have fewer than 200 observations. We assume those data values are missing at random (MAR). 

1. Figure out proportion of missingness for each of those six variables

```{r, echo=FALSE, message=FALSE, error=FALSE}
library(foreign)
library(mi)
ds<-read.csv("hsb_mar.csv")
```

Summary of Missingness:
```{r, echo=FALSE}
Missingness<-c(sum(is.na(ds$FEMALE)), sum(is.na(ds$PROG)), sum(is.na(ds$READ)), 
                   sum(is.na(ds$WRITE)), sum(is.na(ds$MATH)), sum(is.na(ds$SCIENCE)))

Variables<-c("FEMALE", "PROG", "READ", "WRITE", "MATH", "SCIENCE")

MissingnessProportion<-Missingness/200

dsMissingnessTable<-cbind(Variables, Missingness, MissingnessProportion)
dsMissingnessTable

```

2. Now you would like to use write, read, math and female to predict socst. 

a). Run the regression analysis using all complete cases

Regressing SOCST onto WRITE, READ, MATH, FEMALE after applying listwise deletion to the dataset.
This left us with a data set of 117 subjects.
```{r, echo=FALSE}
dsComplete<-na.omit(ds)
ModelComplete<-glm(SOCST~WRITE+READ+MATH+FEMALE, data=dsComplete)
summary(ModelComplete)
```

b).Run the regression analysis using multiple imputed data sets (nimpute = 5)

```{r, echo=TRUE, message=FALSE, results='hide'}
dsInfo<-mi.info(ds)
dsMI<-mi(object=ds, info=dsInfo, n.imp=5)
fit<-lm.mi(SOCST~WRITE+READ+MATH+FEMALE, dsMI)
fit@mi.pooled
```

```{r, echo=FALSE}
fit@mi.pooled
```

c). Compare the results from (a) and (b). What did you find? 

The regression coefficients associated with "FEMALE", and to a lesser extent "READ", have increased noticeably, although their
standard errors seem unchanged. It seems that the MI process has increased the correlation between the predictor variables "FEMALE" and "READ" and the dependent variable, SOCST. 
The intercept for the imputed dataset has shrunk considerably. 